PeakNet: An Autonomous Bragg Peak Finder with Deep Neural Networks

### 2023-06-30 manuscript.tex
Merged new changes from overleaf.

\begin{table*}[t]
\caption{
    The runtime performance of diffraction image analysis algorithms measured on Rayonix images containing 3.7 megapixels.  We measured runtime performance of \psocake{} and \peaknet{} directly using Rayonix images.  For reference purposes, we also included peak finding method RPF \citep{hadian-jaziPeakfindingAlgorithmBased2017, hadian-jaziDataReductionSerial2021} and Cheetah \citep{bartyCheetahSoftwareHighthroughput2014}, whose runtime performance were originally measured on AGIPD 1M \citep{allahgholiAdaptiveGainIntegrating2019}.
}
\label{tb : runtime}
\centering
\resizebox{!}{!}{
\begin{tabular}{lllcc}
\hline
Methods         &  Auto-mask   & Hardware       & Image dimension    & Time (ms/event) \\ \hline
\peaknet{}      &  Yes         & NVIDIA 1080 Ti & 1920 $\times$ 1920 & 90.0            \\ \hline
\psocake{}      &  No          & Intel E5-2620  & 1920 $\times$ 1920 & 175.5           \\ \hline
RPF             &  No          & Intel E5-2698  & 1024 $\times$ 1024 & 120.0           \\ \hline
Cheetah         &  No          & Intel E5-2698  & 1024 $\times$ 1024 & 120.0           \\ \hline
%CNN hit finder      & Hit Finding  & NVIDIA 1080 Ti & 720 $\times$ 720   & 0.8             \\ \hline
%ORB+MLP             & Hit Finding  & Intel Core i5  & 720 $\times$ 720   & 50.0            \\ \hline
\end{tabular}
}
\end{table*}

>>>>

\begin{table*}[t]
\caption{
    The runtime performance of diffraction image analysis algorithms measured on Rayonix images containing 3.7 megapixels.  We measured runtime performance of \psocake{} and \peaknet{} directly using Rayonix images.  For reference purposes, we also included peak finding methods RPF and Cheetah, whose runtime performance were originally measured on AGIPD 1M \citep{allahgholiAdaptiveGainIntegrating2019}.
}
\label{tb : runtime}
\centering
\resizebox{!}{!}{
\begin{tabular}{lllcc}
\hline
Methods         &  Auto-mask   & Hardware       & Image dimension    & Time (ms/event) \\ \hline
\peaknet{}      &  Yes         & NVIDIA 1080 Ti & 1920 $\times$ 1920 & 90.0            \\ \hline
\psocake{}      &  No          & Intel E5-2620  & 1920 $\times$ 1920 & 175.5           \\ \hline
RPF             &  No          & Intel E5-2698  & 1024 $\times$ 1024 & 120.0           \\ \hline
Cheetah         &  No          & Intel E5-2698  & 1024 $\times$ 1024 & 120.0           \\ \hline
%CNN hit finder      & Hit Finding  & NVIDIA 1080 Ti & 720 $\times$ 720   & 0.8             \\ \hline
%ORB+MLP             & Hit Finding  & Intel Core i5  & 720 $\times$ 720   & 50.0            \\ \hline
\end{tabular}
}
\end{table*}
